\documentclass[12pt,draftclsnofoot,onecolumn,journal]{IEEEtran}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}
\usepackage{booktabs}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}   % bold head, upright roman body
\newtheorem{remark}{Remark}
\newcommand{\BSC}{\mathsf{BSC}}
\newcommand{\ind}[1]{\mathbf{1}_{#1}}

\title{The Most Informative Boolean Function Conjecture Holds for $n = 4$}
\author{%
  [Author list TBD]\thanks{%
  Code and verification artifacts:
  \url{https://github.com/gokhanmergen/information-theory-problems}.}}

\begin{document}

\markboth{Draft --- not submitted (July 2026)}%
{The Most Informative Boolean Function Conjecture Holds for $n=4$}

\maketitle

\begin{abstract}
Let $X$ be uniform on $\{0,1\}^n$ and let $Y$ be the output of a memoryless
binary symmetric channel with crossover probability $\alpha$ on input $X$.
Courtade and Kumar conjectured that every Boolean function
$f:\{0,1\}^n\to\{0,1\}$ satisfies $I(f(X);Y)\le 1-h(\alpha)$, where $h$ is the
binary entropy function: no one-bit quantization of $X$ is more informative
about the noisy observation than a single coordinate. We prove the conjecture
for $n=4$ and every $\alpha\in(0,\tfrac12)$, with dictators and anti-dictators
the unique maximizers on $[0.001,0.495]$. To our knowledge this is the first
rigorous full-noise-range verification for arbitrary Boolean functions at a
fixed $n$. The proof is computer-assisted but self-contained: two short
analytic lemmas handle neighborhoods of the degenerate endpoints
$\alpha\to0$ and $\alpha\to\tfrac12$, with their finitely many per-class
hypotheses verified in exact rational arithmetic, and validated interval
arithmetic certifies the strict inequality on the compact middle range, class
by class over the $222$ NPN equivalence classes of $4$-variable Boolean
functions. An explicit covering lemma assembles the regimes. All computations
are reproducible from the public repository.
\end{abstract}

\begin{IEEEkeywords}
Boolean functions, binary symmetric channel, computer-assisted proof,
Courtade--Kumar conjecture, interval arithmetic, mutual information.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}

\IEEEPARstart{H}{ow} much can a single bit reveal about a noisy vector? Let
$X\sim\mathrm{Uniform}(\{0,1\}^n)$ and let $Y$ be obtained from $X$ by
passing each coordinate independently through $\BSC(\alpha)$,
$\alpha\in(0,\tfrac12)$. Every Boolean function $f:\{0,1\}^n\to\{0,1\}$ is a
one-bit quantization of the clean data, and data processing alone bounds its
relevance to the noisy observer only by
$I(f(X);Y)\le\min\{1,\,n(1-h(\alpha))\}$. Courtade and Kumar~\cite{CK14}
conjectured the far sharper
\begin{equation}\label{eq:ck}
I(f(X);Y)\;\le\;1-h(\alpha)
\end{equation}
for every Boolean $f:\{0,1\}^n\to\{0,1\}$, with the dictator functions
$f(x)=x_i$ and their complements (anti-dictators) achieving equality: the most
informative one-bit summary is a single coordinate. The question arose from
CEO-style distributed inference problems~\cite{CK14}, and \eqref{eq:ck} is a
fundamental limit on the usefulness of a hard decision, made from clean data,
to a remote observer who sees only noise-corrupted data. Beyond its
operational content, the conjecture has become a benchmark for the interaction
of information theory with the analysis of Boolean functions: a one-line,
finite-dimensional statement that has resisted hypercontractivity, Fourier
perturbation, and isoperimetric methods for over a decade.

\subsection{Related work}

The conjecture remains open in general. Among peer-reviewed results: it holds
in the high-noise regime $\alpha\in[\tfrac12-\delta,\tfrac12)$ for an
inexplicit absolute constant $\delta$~\cite{Samorodnitsky16}; improved global
bounds short of \eqref{eq:ck} appear in~\cite{OSW16}; the conjecture is
equivalent to a symmetrized Li--M\'edard conjecture~\cite{BO20}; and a
differential-equation reformulation reduces the balanced case to a
finite-dimensional functional inequality~\cite{CGN25}. Yu~\cite{Yu24}
established local optimality of dictators and, combining it with earlier
bounds and computer-assisted estimates, confirmed the \emph{balanced}
conjecture for the explicit correlation range $\rho=1-2\alpha\in[0,0.914]$,
uniformly in $n$. Among preprints, Javanmard and Woodruff~\cite{JW26}
sharpened the high-noise entropy expansion to its optimal order and proved a
coordinate-wise form of \eqref{eq:ck} for all Boolean functions, again with
inexplicit constants delimiting the proven range. Two claimed full proofs
were later withdrawn by their authors~\cite{Kesal15,Sarbu16}. As numerical
evidence, Courtade and Kumar~\cite[Sec.~II-B]{CK14} enumerated compressed
Boolean functions through $n=7$ and evaluated their mutual information;
separately, their implementation of Algorithm~II.1 sampled a related
inequality on a noise grid of spacing $0.001$~\cite[Sec.~II-D]{CK14}. Neither
computation proves \eqref{eq:ck} on any noise interval.

For \emph{arbitrary} (including unbalanced) Boolean functions at a fixed $n$,
no proof covering the entire range $(0,\tfrac12)$ appears to have been
recorded: the high-noise theorems have inexplicit constants, so they cannot
be concatenated with grid computations; and the low-noise limit --- where
\eqref{eq:ck} degenerates to equality for every balanced $f$ at $\alpha=0$
--- has no general theorem at all.

\subsection{Contribution}

\begin{theorem}\label{thm:main}
For $n=4$, inequality~\eqref{eq:ck} holds for every $\alpha\in(0,\tfrac12)$ and
every Boolean function $f$. Moreover, for $\alpha\in[0.001,0.495]$, equality
holds if and only if $f$ is a dictator or an anti-dictator.
\end{theorem}

The endpoint regimes are exactly where naive certification must fail: the gap
$g_f(\alpha):=1-h(\alpha)-I(f(X);Y)$ vanishes as $\alpha\to\tfrac12$ for every
$f$, and as $\alpha\to0$ for every balanced $f$. Our two endpoint lemmas
isolate the finite data controlling \eqref{eq:ck} there.

\textbf{Endpoint regimes.} Edge-boundary profiles and hypercube
edge-isoperimetry control the conjecture near $\alpha=0$; level-one Fourier
weight and spectral $\ell_1$-mass control it near $\alpha=\tfrac12$. Each
endpoint reduces to finitely many rational inequalities, verified exactly.

\textbf{Middle range.} Validated interval arithmetic certifies strict
inequality on the compact middle range, class by class
(Section~\ref{sec:certify}).

\textbf{Complete coverage.} Lemma~\ref{lem:cover} assembles the regimes into
a gap-free cover of $(0,\tfrac12)$. The scheme is dimension-generic;
Section~\ref{sec:discussion} reports its state at $n=5$.

\begin{remark}[Scope of the uniqueness claim]\label{rem:unique}
The interval computation certifies \emph{strict} inequality for every
non-dictator class on $[0.001,0.495]$, which yields the equality
characterization there. The endpoint lemmas establish $g_f\ge0$ without a
uniform separating margin, so uniqueness on $(0,0.001)\cup(0.495,\tfrac12)$
is expected but not certified here; no non-dictator equality case can occur
on the certified range, and we know of no mechanism producing one in the
endpoint slivers.
\end{remark}

\section{Setup, symmetry reduction, and class accounting}\label{sec:setup}

Throughout, $h(u)=-u\log_2 u-(1-u)\log_2(1-u)$ with the convention
$0\log_20:=0$; $\rho=1-2\alpha$. Write $q_1=\Pr[f(X)=1]=|f^{-1}(1)|/16$ and
$q_0=1-q_1$; neither depends on $\alpha$. Since $Y$ is uniform on
$\{0,1\}^4$,
\[
g_f(\alpha)=H\bigl(f(X),Y\bigr)(\alpha)-h(\alpha)-3-H(q_1),
\]
and the $2\times16$ joint probabilities are the exact polynomials
\[
p_{v,y}(\alpha)=2^{-4}\sum_{d=0}^{4}c_{v,y,d}\,\alpha^d(1-\alpha)^{4-d},
\qquad
c_{v,y,d}=\#\{x:\ f(x)=v,\ d_H(x,y)=d\},
\]
where $d_H$ is Hamming distance; this uses that, given $Y=y$, the posterior
of $X$ is the product BSC kernel centered at $y$ (Bayes' rule with uniform
input and a symmetric channel).

$I(f(X);Y)$ is invariant under permutations of the coordinates, flips of
input coordinates, and complementation of the output, so it suffices to prove
\eqref{eq:ck} for one representative of each NPN equivalence class. For
$n=4$ there are $222$ classes~\cite{Harrison65}, a count our enumeration
reproduces, with orbit sizes summing to $2^{16}$. The accounting used
throughout is given in Table~\ref{tab:accounting}.
\begin{table}[t]
\centering
\caption{Disposition of the 222 NPN classes.}
\label{tab:accounting}
\begin{tabular}{lll}
\toprule
\textbf{Classes} & \textbf{Method} & \textbf{Conclusion}\\
\midrule
$1$ constant & analytic: $I=0$ & $g_f=1-h(\alpha)>0$\\
$1$ dictator & analytic: $I=1-h(\alpha)$ & $g_f\equiv0$ (equality)\\
$220$ remaining & Lemmas~\ref{lem:low}, \ref{lem:high}; Proposition~\ref{prop:cert} & $g_f>0$ (middle), $g_f\ge0$ (endpoints)\\
\bottomrule
\end{tabular}
\end{table}
Every computer-assisted step below covers the same $220$ classes; the
interval certification additionally re-verifies the constant class (whose
zero $c_{v,y,d}$ counts drop out of the entropy sum by the $0\log_20$
convention), which is why its logs report $221$.

\section{The low-noise lemma}

For $y\in\{0,1\}^4$ let $b_y$ be the number of Hamming neighbors $x$ of $y$
with $f(x)\neq f(y)$, and set $c_1=\tfrac1{16}\sum_y b_y$ (so $16c_1=2B$ with
$B$ the edge boundary of $f^{-1}(1)$) and
$c_2=\tfrac1{16}\sum_y b_y\log_2 b_y$ (terms with $b_y=0$ vanish by the
$0\log_20$ convention; $b_y\le4$ gives $c_2\le2c_1$).

\begin{lemma}[code-verified enumeration]\label{lem:boundary}
Over the balanced NPN classes of $Q_4$, the minimum edge boundary of a
non-dictator class is $12$; dictators attain the edge-isoperimetric minimum
$8$, uniquely among balanced sets.
\end{lemma}

The uniqueness of subcubes at the edge-isoperimetric minimum is classical
\cite{Lindsey64,Harper64,Bernstein67,Hart76}; the value $12$ for the best
balanced non-dictator is an exhaustive computation over the balanced classes,
recorded in the repository (it is not claimed to follow from the
isoperimetric theorems).

\begin{lemma}\label{lem:low}
Let $\alpha\in(0,10^{-3}]$, $t=\log_2(1/\alpha)$, $t_0=\log_2 1000$,
$\gamma=(1-10^{-3})^3$. If $f$ is balanced and
$t_0(\gamma c_1-1)\ge \log_2 e+c_2$, or $f$ is unbalanced and
$10^{-3}\bigl[t_0\max(0,1-\gamma c_1)+\log_2 e+c_2\bigr]\le 1-H(q_1)$,
then $g_f(\alpha)\ge 0$.
\end{lemma}

\begin{proof}
Write $g_f=m_0-D(\alpha)$ with $m_0=1-H(q_1)$ and
$D(\alpha)=h(\alpha)-H(f(X)\mid Y)$. Three elementary steps:

\textbf{(i)} $H(f(X)\mid Y{=}y)=h(\Pr[f(X)\neq f(y)\mid y])$, and
$\Pr[f(X)\neq f(y)\mid y]\ge b_y\,\alpha(1-\alpha)^3=:b_y\beta$ by keeping
only the distance-one terms of the posterior kernel. Both quantities are at
most $\Pr[X\ne y\mid Y{=}y]=1-(1-\alpha)^4\le4\alpha\le\tfrac12$, and $h$ is
increasing on $[0,\tfrac12]$, so
$H(f(X)\mid Y)\ge\tfrac1{16}\sum_y h(b_y\beta)$.

\textbf{(ii)} $h(u)\ge u\log_2(1/u)$ for $u\in[0,1]$, hence
$h(b_y\beta)\ge b_y\beta\,[t-\log_2 b_y]$ using $\beta\le\alpha$.

\textbf{(iii)} $h(\alpha)\le\alpha(t+\log_2 e)$, from
$(1-\alpha)\ln\frac1{1-\alpha}\le\alpha$.

Combining, and applying $\beta\ge\gamma\alpha$ to the aggregate
$c_1t-c_2$ --- which is nonnegative since $c_2\le2c_1$ and $t\ge t_0>2$ ---
while bounding the residual $c_2$ term with $\beta\le\alpha$:
\[
D(\alpha)\;\le\;\alpha\bigl[\,t(1-\gamma c_1)+\log_2 e+c_2\,\bigr].
\]
If $f$ is balanced then $m_0=0$ and $c_1\ge\tfrac32$ by
Lemma~\ref{lem:boundary}; the $t$-coefficient is negative and $t\ge t_0$
gives the stated criterion. If $f$ is unbalanced, $\alpha t$ is increasing on
$(0,1/e)$, so $D$ is maximized at $\alpha=10^{-3}$, giving the stated
criterion against $m_0>0$.
\end{proof}

All $220$ classes satisfy the applicable criterion, verified in exact
rational arithmetic with two-sided rational enclosures of
$\log_23,\log_25,\log_27,\log_211,\log_213,\log_2e,\log_21000$ (each proved
by integer exponentiation or a rational series, and used in the unfavorable
direction). The minimum slack over all classes is
$1680/546377\approx3.1\times10^{-3}$, attained by class \texttt{0x1669}
($q_1=7/16$); no class is borderline.

\section{The high-noise lemma}

Fourier conventions: for $S\subseteq\{1,\dots,4\}$ let
\[
\chi_S(y)=(-1)^{\sum_{i\in S}y_i},\qquad
\widehat{\ind f}(S)=2^{-4}\sum_x\ind f(x)\chi_S(x),
\]
so $\ind f=\sum_S\widehat{\ind f}(S)\chi_S$ and the noise operator satisfies
$T_\rho\ind f=\sum_S\widehat{\ind f}(S)\rho^{|S|}\chi_S$ with
$T_\rho\ind f(y)=\Pr[f(X)=1\mid Y=y]$. Parseval gives
$\sum_S\widehat{\ind f}(S)^2=2^{-4}\sum_x\ind f(x)^2=q_1$ and hence
$\sum_{S\neq\emptyset}\widehat{\ind f}(S)^2=q_1-q_1^2=q_0q_1$. Define
$\widetilde W_1=\sum_{|S|=1}\widehat{\ind f}(S)^2/(q_0q_1)\in[0,1]$,
$A=\sum_{S\neq\emptyset}|\widehat{\ind f}(S)|$, and
$q_{\min}=\min(q_0,q_1)$. Constants have $q_{\min}=0$ and are excluded; they
were handled in Section~\ref{sec:setup}.

\begin{lemma}\label{lem:high}
Let $\rho_0=10^{-2}$. If $\rho_0A/q_{\min}\le\tfrac12$ and
\[
\bigl[\widetilde W_1+\rho_0^2(1-\widetilde W_1)\bigr]
\bigl(1+\tfrac43\rho_0A/q_{\min}\bigr)\;\le\;1,
\]
then $g_f(\alpha)\ge0$ for all $\rho\in(0,\rho_0]$.
\end{lemma}

\begin{proof}
Write $p(v,y)=q_v2^{-4}(1+\varepsilon_{v,y})$. Since
$p(1,y)=2^{-4}T_\rho\ind f(y)$ and $p(0,y)=2^{-4}(1-T_\rho\ind f(y))$,
\[
\varepsilon_{1,y}=\frac{T_\rho\ind f(y)-q_1}{q_1},\qquad
\varepsilon_{0,y}=-\frac{T_\rho\ind f(y)-q_1}{q_0},
\]
and $|T_\rho\ind f(y)-q_1|\le\sum_{S\ne\emptyset}|\widehat{\ind f}(S)|
\rho^{|S|}\le\rho A$ for $\rho\le1$, so
$|\varepsilon_{v,y}|\le\rho A/q_{\min}=:\varepsilon_{\max}$. By Parseval,
\[
\chi^2:=\sum_{v,y}q_v2^{-4}\varepsilon_{v,y}^2
=\frac{\sum_{S\neq\emptyset}\widehat{\ind f}(S)^2\rho^{2|S|}}{q_0q_1}
\le\rho^2\bigl[\widetilde W_1+\rho^2(1-\widetilde W_1)\bigr],
\]
using $\rho^{2|S|}\le\rho^4$ for $|S|\ge2$. For $|\varepsilon|\le\tfrac12$,
$(1+\varepsilon)\ln(1+\varepsilon)\le\varepsilon+\tfrac{\varepsilon^2}2
+\tfrac23|\varepsilon|^3$: the series
$(1+\varepsilon)\ln(1+\varepsilon)=\varepsilon+\sum_{k\ge2}
\frac{(-1)^k\varepsilon^k}{k(k-1)}$ is, for $\varepsilon\ge0$, alternating
with decreasing terms after $\varepsilon^2/2$ (negative leading tail term),
and for $\varepsilon\in[-\tfrac12,0)$ all terms are positive with tail at
most $\tfrac{|\varepsilon|^3}{6}\cdot\frac1{1-|\varepsilon|}
\le\tfrac{|\varepsilon|^3}3$. Since
$\sum_{v,y}q_v2^{-4}\varepsilon_{v,y}=0$ (both marginals are exact), summing
gives $I(f(X);Y)\ln2\le\tfrac{\chi^2}2(1+\tfrac43\varepsilon_{\max})$.
Finally $1-h(\alpha)=\frac1{\ln2}\sum_{k\ge1}\frac{\rho^{2k}}{2k(2k-1)}
\ge\frac{\rho^2}{2\ln2}$ with all series terms positive. Because
$1-\widetilde W_1\ge0$, both bracketed factors in the hypothesis are
nondecreasing in $\rho$, so verification at $\rho_0$ suffices for all
$\rho\in(0,\rho_0]$.
\end{proof}

All $220$ classes pass, including all balanced ones, with exact dyadic
Fourier data; no external high-noise theorem is invoked. The maximum
$\widetilde W_1$ over non-dictator classes is $52/63$ (a dictator altered on
a single input), and the minimum slack of the lemma's hypothesis is
$0.1416$, attained by that same class; no class is borderline.

\section{Validated computation on the middle range}\label{sec:certify}

\begin{proposition}\label{prop:cert}
For every one of the $221$ NPN representatives (the $220$ classes plus the
constant class) and every subinterval recorded in the certification runs
below, the outward-rounded interval evaluation of $g_f$ encloses the true
range of $g_f$ on that subinterval, its infimum is positive, and the recorded
subintervals cover $[10^{-3},0.0055]\cup[0.005,0.495]$ together with the
exact-rational bridges $[9/10^4,11/10^4]$ and $[4949/10^4,4951/10^4]$.
\end{proposition}

\paragraph{Enclosure validity} The proposition rests on five ingredients:
\begin{itemize}
\item \textbf{NPN reduction correctness:} Section~\ref{sec:setup}; class
count and orbit sum checked against \cite{Harrison65}.
\item \textbf{Polynomial exactness:} the integer-coefficient polynomials
$p_{v,y}$ are constructed exactly.
\item \textbf{Enclosure properties:} each interval operation used ---
addition, multiplication, division, and logarithm in \texttt{mpmath.iv} at
$90$-bit precision --- is outward-rounded; only these operations are used,
and although \texttt{mpmath} labels interval support experimental, this
elementary-operation path is deterministic and regression-tested in the
repository.
\item \textbf{Adaptive bisection:} a subinterval is discharged only when
the enclosure's \emph{infimum} is positive.
\item \textbf{Recorded ledgers} for every discharged subinterval.
\end{itemize}

\paragraph{Implementation and runtime} $2029$\,s and $2.6$\,s
single-threaded (Python 3.14, \texttt{mpmath} 1.3.0, macOS/arm64).

\paragraph{Reproducibility} The trusted computing base beyond
\texttt{mpmath} is a ${\sim}30$-line enclosure routine printed in the
repository.

\paragraph{Archival status} An immutable archived release with a
machine-readable per-subinterval certificate and an independent certificate
checker is planned before submission. The audit history, including a repaired
floating-point endpoint defect that motivated the two bridges, is in
Appendix~\ref{app:audit}.

\section{Covering the noise interval}

\begin{lemma}\label{lem:cover}
Every $\alpha\in(0,\tfrac12)$ lies in at least one verified regime, and
consecutive regimes overlap on sets of positive measure:
\[
(0,\tfrac12)\;=\;
\underbrace{(0,10^{-3}]}_{\text{Lem.~\ref{lem:low}}}
\;\cup\;\underbrace{[\tfrac{9}{10^4},\tfrac{11}{10^4}]}_{\text{bridge}}
\;\cup\;\underbrace{[10^{-3},0.0055]\cup[0.005,0.495]}_{\text{Prop.~\ref{prop:cert} runs}}
\;\cup\;\underbrace{[\tfrac{4949}{10^4},\tfrac{4951}{10^4}]}_{\text{bridge}}
\;\cup\;\underbrace{[0.495,\tfrac12)}_{\text{Lem.~\ref{lem:high}}}.
\]
\end{lemma}

\begin{proof}
The union contains $(0,\tfrac12)$ by inspection of the rational endpoints;
the overlaps $(0,10^{-3}]\cap[\tfrac9{10^4},\tfrac{11}{10^4}]$,
$[\tfrac9{10^4},\tfrac{11}{10^4}]\cap[10^{-3},0.0055]$, $[0.005,0.0055]$,
$[0.4949,0.495]$, and $[0.495,0.4951]$ all have positive length. The bridges
are certified with exactly represented rational endpoints, eliminating any
dependence on the floating-point endpoint handling of the two main runs
(Appendix~\ref{app:audit}).
\end{proof}

Theorem~\ref{thm:main} follows: constants and dictators are analytic
(Section~\ref{sec:setup}); every other class satisfies $g_f\ge0$ on the
endpoint regimes (Lemmas~\ref{lem:low}, \ref{lem:high}) and $g_f>0$ on the
middle range (Proposition~\ref{prop:cert}); and the regimes cover
$(0,\tfrac12)$ (Lemma~\ref{lem:cover}). The uniqueness statement is
Remark~\ref{rem:unique}.

\section{Discussion}\label{sec:discussion}

The four-regime scheme is dimension-generic. At $n=5$ there are $616{,}126$
NPN classes --- roughly three orders of magnitude more than at $n=4$ --- and
the two endpoint lemmas have already been verified for all of them in exact
arithmetic (with the low-noise cutover moved to $10^{-4}$, as the
near-balanced margins shrink); the middle-range certification is
embarrassingly parallel by class and is in progress. The genuinely new
difficulty as $n$ grows is quantitative: the dictator's isolation gap
shrinks (single flips carry input mass $2^{-n}$), so the certified middle
range must push closer to the endpoints, where the lemmas' margins ---
edge-isoperimetric at low noise, spectral at high noise --- grow more
robust. Formal verification (e.g., in Lean) of the two finite endpoint
checks is a natural hardening step: the per-class conditions are pure
rational arithmetic over explicitly listed data.

\section*{Contribution and AI-Use Statement}

In accordance with IEEE policy on AI-generated content:

\textbf{Initial generation.} The proof strategy, the two endpoint lemmas,
all code, and the initial manuscript draft were produced by an AI system
(Claude Fable 5, Anthropic) operating on a public open-problems repository.

\textbf{Independent audit and repair.} A separate AI system (GPT-5 Codex,
OpenAI) performed adversarial audits that identified the endpoint defect and
a citation-provenance correction recorded in Appendix~\ref{app:audit}, and
repaired the certification script.

\textbf{Validation of the proofs.} The endpoint lemma conditions and the
manuscript's mathematical claims were independently validated by Gemini 3.5
Flash (Google) and ChatGPT 5.6 Sol (OpenAI).

\textbf{Human responsibility.} The human maintainer supervised the process,
reviewed the mathematics, and is responsible for the content. AI-generated
material appears throughout the manuscript. AI audit does not substitute for
independent human verification; readers are invited to check the two lemmas
by hand (they are elementary) and to re-run the public code.

\appendices

\section{Audit History and Validation}\label{app:audit}

The artifact was adversarially audited before being recorded; two findings
are material. First, the script used for the two recorded interval runs
converted its decimal endpoint strings to binary floating point before
intervalization, rounding $0.001$ upward by $2.08\times10^{-20}$ and $0.495$
downward by $4.44\times10^{-18}$; the recorded runs therefore covered two
microscopically shortened intervals. The repaired script keeps all endpoints
as exact rationals until evaluation, and the two rational-endpoint bridges
of Lemma~\ref{lem:cover} independently certify neighborhoods of both seams,
so the covering argument does not depend on the original endpoint handling.
Second, an earlier internal review proposed an alternative high-noise proof
by discarding a fourth-order Taylor remainder; that argument has the wrong
inequality direction ($h^{(4)}<0$ makes the corresponding contribution to
mutual information positive) and is not used anywhere: the high-noise regime
rests solely on Lemma~\ref{lem:high}. The hard-coded logarithm enclosures
used by the exact-rational checks are themselves proved by integer
exponentiation (e.g., $2^{a}\le n^{b}$) or a truncated rational series for
$\ln2$, in a self-test that runs before every verification.

\begin{thebibliography}{99}
\bibitem{CK14} T.~A. Courtade and G.~R. Kumar, ``Which Boolean functions
maximize mutual information on noisy inputs?'' \emph{IEEE Trans.\ Inf.\
Theory}, 60(8):4515--4525, 2014.
\bibitem{Samorodnitsky16} A.~Samorodnitsky, ``On the entropy of a noisy
function,'' \emph{IEEE Trans.\ Inf.\ Theory}, 62(10):5446--5464, 2016.
\bibitem{OSW16} O.~Ordentlich, O.~Shayevitz, and O.~Weinstein, ``An improved
upper bound for the most informative Boolean function conjecture,''
\emph{Proc.\ IEEE ISIT}, 2016.
\bibitem{Yu24} L.~Yu, ``Local optimality of dictator functions with
applications to Courtade--Kumar and Li--M\'edard conjectures,''
arXiv:2410.10147; to appear, \emph{Ann.\ Appl.\ Probab.}
\bibitem{JW26} A.~Javanmard and D.~P. Woodruff, ``Progress on the
Courtade--Kumar conjecture: optimal high-noise entropy bounds and
generalized coordinate-wise mutual information,'' arXiv:2601.09679, 2026.
\bibitem{BO20} L.~Barnes and A.~\"Ozg\"ur, ``The Courtade--Kumar most
informative Boolean function conjecture and a symmetrized Li--M\'edard
conjecture are equivalent,'' \emph{Proc.\ IEEE ISIT}, 2020.
\bibitem{CGN25} Z.~Chen, A.~Gohari, and C.~Nair, ``A differential equation
approach to the most-informative Boolean function conjecture,''
\emph{Proc.\ IEEE ISIT}, 2025; arXiv:2502.10019.
\bibitem{Kesal15} M.~Kesal, arXiv:1511.01828 (withdrawn).
\bibitem{Sarbu16} S.~S\^arbu, arXiv:1604.05113 (withdrawn).
\bibitem{Harrison65} M.~A. Harrison, \emph{Introduction to Switching and
Automata Theory}, McGraw--Hill, 1965 (NPN classification of Boolean
functions).
\bibitem{Lindsey64} J.~H. Lindsey~II, ``Assignment of numbers to vertices,''
\emph{Amer.\ Math.\ Monthly}, 71(5):508--516, 1964.
\bibitem{Harper64} L.~H. Harper, ``Optimal assignments of numbers to
vertices,'' \emph{J.\ SIAM}, 12(1):131--135, 1964.
\bibitem{Bernstein67} A.~J. Bernstein, ``Maximally connected arrays on the
$n$-cube,'' \emph{SIAM J.\ Appl.\ Math.}, 15(6):1485--1489, 1967.
\bibitem{Hart76} S.~Hart, ``A note on the edges of the $n$-cube,''
\emph{Discrete Math.}, 14(2):157--163, 1976.
\end{thebibliography}

\end{document}
